\clearpage
\begin{centering}
\textbf{ACKNOWLEDGEMENTS}\\
\vspace{\baselineskip}
\end{centering}

%Insert your dedication text here
First and foremost, I am grateful to God for blessing me with good health, vitality, and strength to accomplish this goal which I ever dreamed of. \\
I extend my sincerest gratitude to my supervisors,  Prof. Pietro Savazzi for his guidance and encouragement during the entire period of Ph.D. I am especially thankful to him for his thought-provoking assistance to solve the research problem. His guidance, knowledge, and expertise have improved my research skills, ability to think critically and deal with challenging situations. I am privileged and I consider myself lucky to be his research student. I am also very thankful to Anna Vizziello for assisting me in my research work. The guidance and assistance which she has provided, including suggestions, reviewing my papers, making modifications, keeping my morale high and all her nice and warm words are ineffable and it improved my technical and research skills.  \\
Particularly, many thanks to  Prof. Fabio Dell'Acqua for his support and help during the time of my Ph.D. I have learned many things from him including methodologies of scientific research as well as analytical and critical thinking.  All these will surely benefit me throughout my career.
I am grateful to Prof. Lorenzo Favalli and Paolo Gamba for reviewing my work during lab meetings and providing valuable suggestions and feedback.  \\
Finally, my family support without which I would never be able to achieve this goal.  My parents who prayed for me and encouraged me for doing this work. My caring and supportive husband who cheered me during a tough time,  restored me and kept me moving when it seemed difficult. My lovely daughters Fatimah, Hanniyah, and Malikha, my inlaws who always boosted me when I was feeling low. 

\clearpage
%\pagenumbering{gobble}  %remove page number on summary page
